\sout{Rare-event sampling applied to the simulation of extreme mechanical efforts exerted by a turbulent flow on a bluff body} \ZZ{Numerical study of extreme mechanical efforts exerted by a turbulent flow on a bluff body by direct and rare-event sampling techniques}

### 2020-01-28 jfm/draft_p2_jfm.tex
Add new figure IS_GKTL_2

%We discussed previously the phenomenology of extreme fluctuations of the \emph{instantaneous} drag and pointed out that the time scale associated with the development of such event is of the order of the sweeping time of the flow past the obstacle $\tau_c$.
We discussed previously the phenomenology of extreme fluctuations of the \emph{instantaneous} drag, and identified the sweeping time of the flow past the obstacle as the characteristic lifetime of these events.
%
In applications, this duration may be much smaller than the response time of the material structure subject to these fluctuations, justifying a practical interest in the averaged (in time) drag force.
% Consider for instance the interaction of a deformable structure with a turbulent flow: the typical response time may be much larger than the lifetime of drag fluctuations.
%
% definition
%
Therefore, a relevant observable is the \textit{time-averaged} drag defined as
\begin{equation}
\label{eq:def_time_averaged_drag}
F_T(t) = \frac{1}{T}\int_t^{t+T} f_d(t) \mathrm{d}t,
\end{equation}
where $f_d(t)$ denotes the instantaneous drag and $T$ is the investigated timescale (response time).
Relevant values of $T$ are application dependant.
We shall consider $T=10\tau_c$ in the following.
\EL{In that case, the PDF of $F_T$ is found nearly Gaussian as a consequence of the Central Limit theorem (see Fig.~\ref{fig:IS_GKTL}).}

@@

Figure~\ref{sec:IS_GKTL} shows the histogram of the values of the average drag $F_{T_a} = \frac{1}{T_a}\int_{0}^{T_a}f_d(t)\mathrm{d}t$ for three ensemble of trajectories sampled with three different values of the cloning strength $k$.
It illustrates that the algorithm effectively samples preferentially trajectories with a higher value of the average.
The higher $k$, the stronger the bias.
The grey histogram represents the average histogram that would be obtained using a direct approach -- \textit{i.e.} with $k=0$ -- for the same computational cost.
We computed this histogram by approximating the \ac{pdf} of the drag averaged over $10\tau_c$ as a Gaussian \ac{pdf} (see figure~\ref{fig:pdf_avg}).
Figure~\ref{sec:IS_GKTL} also illustrates that the sampling by the algorithm is very concentrated on some fluctuations values, and that this effect increases as $k$ increases.
This results from the overlap of trajectories as a consequence of the cloning and pruning.
Indeed, if a trajectory is cloned at step $i$, then the trajectory ${\mathbf{x}(t)}$ over the interval $[0;i\tau]$ will be the same for all the clones.
For a fixed ensemble size $N$, the overlap of trajectories increases as $k$ increases as fewer
trajectories are cloned into a higher number of duplicates.
\textbf{How do we quantify this effect? It is probably application-dependant. What are the strategies to mitigate it?}

>>>>

%We discussed previously the phenomenology of extreme fluctuations of the \emph{instantaneous} drag and pointed out that the time scale associated with the development of such event is of the order of the sweeping time of the flow past the obstacle $\tau_c$.
We discussed previously the phenomenology of extreme fluctuations of the \emph{instantaneous} drag, and identified the sweeping time of the flow past the obstacle as the characteristic lifetime of these events.
%
In applications, this duration may be much smaller than the response time of the material structure subject to these fluctuations, justifying a practical interest in the averaged (in time) drag force.
% Consider for instance the interaction of a deformable structure with a turbulent flow: the typical response time may be much larger than the lifetime of drag fluctuations.
%
% definition
%
Therefore, a relevant observable is the \textit{time-averaged} drag defined as
\begin{equation}
\label{eq:def_time_averaged_drag}
F_T(t) = \frac{1}{T}\int_t^{t+T} f_d(t) \mathrm{d}t,
\end{equation}
where $f_d(t)$ denotes the instantaneous drag and $T$ is the investigated timescale (response time).
Relevant values of $T$ are application dependant.
We shall consider $T=10\tau_c$ in the following.
\EL{In that case, the PDF of $F_T$ is found nearly Gaussian as a consequence of the Central Limit theorem (see Fig.~\ref{fig}).}

@@

\begin{figure}
  \centering
  \includegraphics[width=.7\linewidth]{IS_GKTL/IS_GKTL_2}
  \caption{Histogram of the values of the time-averaged drag $F_{T_a}$, with $T_a = 10\tau_c$, in the ensemble sampled by the cloning algorithm, for three values of the cloning strength $k$. In each case, the algorithm was applied with $N=1024$, $\tau = \tau_c / 2$. The grey histogram represents the average histogram obtained through a direct sampling, \textit{i.e.} with $k=0$. It was computed using a Gaussian approximation for the \ac{pdf} of the time-averaged drag.}
  \label{fig:IS_GKTL}
\end{figure}
Figure~\ref{fig:IS_GKTL} shows the histogram of the values of the average drag $F_{T_a} = \frac{1}{T_a}\int_{0}^{T_a}f_d(t)\mathrm{d}t$ for three ensemble of trajectories sampled with three different values of the cloning strength $k$.
It illustrates that the algorithm effectively samples preferentially trajectories with a higher value of the average.
The higher $k$, the stronger the bias.
The grey histogram represents the average histogram that would be obtained using a direct approach -- \textit{i.e.} with $k=0$ -- for the same computational cost.
We computed this histogram by approximating the \ac{pdf} of the drag averaged over $10\tau_c$ as a Gaussian \ac{pdf} (see figure~\ref{fig:pdf_avg}).
Figure~\ref{sec:IS_GKTL} also illustrates that the sampling by the algorithm is very concentrated on some fluctuations values, and that this effect increases as $k$ increases.
This results from the overlap of trajectories as a consequence of the cloning and pruning.
Indeed, if a trajectory is cloned at step $i$, then the trajectory ${\mathbf{x}(t)}$ over the interval $[0;i\tau]$ will be the same for all the clones.
For a fixed ensemble size $N$, the overlap of trajectories increases as $k$ increases as fewer
trajectories are cloned into a higher number of duplicates.
\textbf{How do we quantify this effect? It is probably application-dependant. What are the strategies to mitigate it?}
